Community Embeddings for Facebook Friend Suggestions\\ \thanks{The reported study was partially supported by RFBR grant \textnumero 20-07-00958. The paper was prepared within the framework of the HSE University Project Group Competition 2020-2022.}

### 2020-10-14 paper-ffs.tex
feedback Opa

The small \textit{Zachary’s Karate Club graph} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the karate club graph \cite{KarateClubDS}.

@@

The top-$N$ friend suggestions, generated for the testing users with Algorithm \ref{alg:friend_sug_com}, are evaluated against the three removed test edges.
The ranked lists of friend-suggestions shown in Table \ref{tab:karateclub_emb_dists} are used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations my the hit-rate metric. The LOO-testing edges are printed bold in Table \ref{tab:karateclub_emb_dists}. The resulting top-$N$ hit-rates are plotted against the number of suggestions $N$ in Fig. \ref{fig:karateclub_hitrates}.

>>>>

The small \textit{Zachary’s Karate Club graph} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the Karate Club graph \cite{KarateClubDS}.

@@

The top-$N$ friend suggestions, generated for the testing users with Algorithm \ref{alg:friend_sug_com}, are evaluated against the three removed test edges.
The ranked lists of friend-suggestions shown in Table \ref{tab:karateclub_emb_dists} are used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations by the hit-rate metric. The LOO-testing edges are printed bold in Table \ref{tab:karateclub_emb_dists}. The resulting top-$N$ hit-rates are plotted against the number of suggestions $N$ in Fig. \ref{fig:karateclub_hitrates}.
